Networked Character Devices

### 2011-12-09 report/presentation.tex
presentation: protocol is a subsection, vim sts
presentation: server subsection and stubs for misc

\section{Protocol}

@@

\begin{frame}[fragile]{Socket Client}
  \begin{itemize}
    \item<1-> socket type: \texttt{AF\_INET}, \texttt{SOCK\_STREAM}, \texttt{IPPROTO\_TCP}
    \begin{itemize}
      \item<2-> should be \texttt{AF\_NETLINK}
      \item<2-> do not want to lose messages
    \end{itemize}
    \item<3-> no familiar \texttt{read()}, \texttt{write()}
  \end{itemize}
\end{frame}

@@

@@

@@

% vim: set sw=2 ts=2 et spell : %

>>>>

\subsection{Protocol}

@@

\begin{frame}{Socket Client}
  \begin{itemize}
    \item<1-> socket type: \texttt{AF\_INET}, \texttt{SOCK\_STREAM}, \texttt{IPPROTO\_TCP}
    \begin{itemize}
      \item<2-> should be \texttt{AF\_NETLINK}
      \item<2-> do not want to lose messages
    \end{itemize}
    \item<3-> no familiar \texttt{read()}, \texttt{write()}
  \end{itemize}
\end{frame}

@@

\begin{frame}[fragile]{Server (\texttt{read()})}
  \begin{lstlisting}[gobble=4]
    struct fop_request req;
    struct fop_reply   rep;
    while (1) {
      err = read(sd, &req, sizeof(req));
      switch(req.call) {
      case FOP_READ:
        payload = realloc(payload, req.count);
        rep.read = read(fd, payload, req.count);
        if (rep.read < 0)
          rep.read = -errno;
        break;
      }
      err = write(sd, &rep, sizeof(rep));
      if (rep.call == FOP_READ && rep.read > 0)
        err = write(sd, payload, rep.read)
    }
  \end{lstlisting}
\end{frame}

@@

\begin{frame}{\texttt{udev}}
\end{frame}

\begin{frame}{\texttt{ncadmin}}
\end{frame}

@@

% vim: set sw=2 ts=2 sts=2 et spell : %
